Combinatorial Identities from Lagrange's Interpolation Polynomial

### 2021-01-07 spectral radius of matrix new method/thesis/article120920.tex
121620 update
010721 read

\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置
%\usepackage{times}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{tabularx,array}
\usepackage{pgf,tikz}
 \usepackage{blkarray} %line 80-92 Q formula matrix index
%\usepackage{colortbl}
\usepackage{enumitem}% enumerate labels   roman
\usepackage{graphicx}
\graphicspath{{images/}}
\usetikzlibrary{arrows}
\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
\date{} %不要日期

@@

%英文摘要
\begin{center}{\LARGE
A simple method on estimating spectral radius for some direted graphs
\bigskip\bigskip\bigskip}

@@

\begin{defn} 
    Given an directed graph G, the$\textit{ adjacency matrix}$ of G is the square 
    matrix $A = (a_{ij})$ indexed by vertices of G, and
     \[a_{ij} =\begin{cases} 
        1, \text{if $i$ is adjacent to $j$}, \\
        0, \text{otherwise.}
            \end{cases}
     \]
\end{defn}

\begin{defn}
    Given a directed graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
     radius of the adjacency matrix of G.
\end{defn}

@@

The next theorem is Perron–Frobenius Theorem, which provides a feature of
 nonnegative eigenvector to nonnegative matrices.
\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
    corresponding nonnegative left eigenvector.
\end{thm}

@@

\section{Our Method}
We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is ${1,2,...,n}$.
Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
appearing in the position $k,n$ of $E_{kn}$. We will apply the previous Theorem \ref{pre_thm} with $P=I$ and

@@

\begin{defn}%[$K$-rooted vector]
~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

Below is our first result, in which the first condition implies the first n-1 columns of C major to
 the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
 suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
  but with the same meaning with Theorem (\ref{pre_thm})
\begin{thm}\label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}[label=(\roman*)]
\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item \label{thm_main:condition_iv}$v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}[label=(\alph*)]
    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} %\qed
\end{thm}
%

@@

We are interested in the matrices $C'$ that have $K$-rooted eigenvectors.
Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions. 
This is the definition of (k,n)-sum.
\begin{defn}
    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
\end{defn}

Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
Below is the definition of k-rooted matrix.
\begin{defn}\label{m_rooted}
    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $K$-rooted except the last column of $C'$.
\end{defn}

@@

The following Theorem shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
\begin{lem}\label{lma_m_rooted}
    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
        \begin{enumerate}[label=(\roman*)]
            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
                for $\rho(C')$. Then  $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$
        \end{enumerate}
\end{lem}

\begin{comment}

\begin{rem}
        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
        1 &  & & &  & 0 \\
         & 1 &  &      &  &  \\
         &  & \ddots & &  & -1 \\
         &  &        & &  &  \\
          &  & & & 1 &  \\
        0 &  & & &  & 1 \\
        \end{pmatrix},$$
\end{rem}
\end{comment}   
\begin{proof}
    (i)
    and $Q^{-1}C'Q$ is
    $$\begin{pmatrix}
    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
    \vdots \\
    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    (ii)
        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $K$-rooted.  
        Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
        $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
        $C'Qu=\rho(C')Qu$.

@@

\begin{proof}
    These assumptions are necessary that $PCQ \leq PC'Q$ where $P = I$,$Q = I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
     (\ref{lma_m_rooted}),\\
    $Q^{-1}C'Q$ = 
    $$\begin{pmatrix}
        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
        \vdots \\
        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    $Q^{-1}C'Q \geq 0$ for that $c'_{kj}\geq c'_{nj}>0$ when $1\leq j\leq n-1$ , $c'_{ij}\geq c_{ij}$ where $C$ is nonnegative,
    and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$\\

    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, \\
    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ \\
    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, \\
    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$ ;\\
    $C'$ is $K$-rooted matrix, then by Lemma (\ref{lma_m_rooted}) Conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3}, there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;\\
    And since $C$ is nonnegative, by Theorem~(\ref{thm:Perron_Frobenius}), which is Perron–Frobenius theorem, we claim there exists
    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ 
    is an eigenvalue of $C$ with associated left eigenvector $v^T$; \\
    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0.$, unless they are orthogonal, i.e, $v^Tv'=0$.\\[1ex]
    Here we can summerize the facts we know so far as the following: \\
    \begin{enumerate}[label=(\roman*)]
        \item  $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
        \item $v^Tv'>0.$
    \end{enumerate}
    which come from Theorem~(\ref{thm_main}).\\
    By Lemma~(\ref{l_diag}), for certain $d$, if $C'+dI$ is $K$-rooted, then it has
    a $K$-rooted eigenvector with its spectral radius $\lambda + d$. $C'$ would share the same
    eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
    conditions of Theorem~(\ref{thm_main}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
    then $\rho(C') \geq \rho(C)$  %\qed
\end{proof}

\subsection{Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    And its corresponding graph,\cite[sage]{sage}\\
    \includegraphics{graph_C.PNG} \\
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$
    also, graph,\cite[sage]{sage}\\
    \includegraphics{graph_Cprime.PNG} \\
    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of Theorem~\ref{thm_main},
    Then
    $\rho(C)\leq \rho(C')$ by previous Theorem~\ref{thm:conclusion}.

>>>>

\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置
%\usepackage{times}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{tabularx,array}
\usepackage{pgf,tikz}
 \usepackage{blkarray} %line 80-92 Q formula matrix index
%\usepackage{colortbl}
\usepackage{enumitem}% enumerate labels   roman
\usepackage{graphicx}
%\usepackage{indentfirst}
\graphicspath{{images/}}
\usetikzlibrary{arrows}
\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
\date{} %不要日期

@@

%英文摘要
\begin{center}{\LARGE
A simple method on estimating spectral radius for some directed graphs
\bigskip\bigskip\bigskip}

@@

\begin{defn} 
    Given an directed graph $G$, the$\textit{adjacency matrix}$ of $G$ is the square 
    matrix $A = (a_{ij})$ indexed by vertices of $G$, and
     \[a_{ij} =\begin{cases} 
        1, \text{if $i$ is adjacent to $j$}, \\
        0, \text{otherwise.}
            \end{cases}
     \]
\end{defn}

\begin{defn}
    Given a directed graph $G$, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
     radius of the adjacency matrix of $G$.
\end{defn}

@@

The next theorem is Perron–Frobenius Theorem, which provides a feature of
 nonnegative eigenvector to nonnegative matrices.
\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
    If $C$ is a nonnegative square matrix, then the spectral radius $\rho(C)$ is an
    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
    corresponding nonnegative left eigenvector.
\end{thm}

@@

\section{Our Method}
We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is $\{1,2,...,n-1\}$.
Throughout fix $k\in [n-1]$. Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
appearing in the position $k,n$ of $E_{kn}$. We will apply the previous Theorem \ref{pre_thm} with $P=I$ and

@@

\begin{defn}%[$K$-rooted vector]
A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

Below is our first result, in which the first condition implies the first $n-1$ columns of $C$ major to
 the columns of $C'$, and the $(k,n)$-sum column of $C$ is also major to $C'$. The second and the third condition
 suggest that $C$ and $C'$ have nonnegative eigenvectors which are $k$-rooted. And the forth condition is simpler
  but with the same meaning with Theorem~(\ref{pre_thm})
\begin{thm}\label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}[label=(\roman*)]
\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item \label{thm_main:condition_iv}$v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}[label=(\alph*)]
    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} %\qed
\end{thm}
%

@@

We are interested in the matrices $C'$ that have $K$-rooted eigenvectors.
Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions. 
This is the definition of $(k,n)$-sum.
\begin{defn}
    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
\end{defn}

Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$.
Below is the definition of $k$-rooted matrix.
\begin{defn}\label{m_rooted}
    A  matrix $C'=(c'_{ij})$ is called $k-rooted$ if its columns and its $(k,n)$-sum vector are all $K$-rooted except the last column of $C'$.
\end{defn}

@@

The following lemma shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
\begin{lem}\label{lma_m_rooted}
    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
        \begin{enumerate}[label=(\roman*)]
            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
                for $\rho(C')$. Then $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$
        \end{enumerate}
\end{lem}

\begin{comment}
\begin{rem}
        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
        1 &  & & &  & 0 \\
         & 1 &  &      &  &  \\
         &  & \ddots & &  & -1 \\
         &  &        & &  &  \\
          &  & & & 1 &  \\
        0 &  & & &  & 1 \\
        \end{pmatrix},$$
\end{rem}
\end{comment}   
\begin{proof}
    (i)
    and $Q^{-1}C'Q$ is
    $$\begin{pmatrix}
    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
    \vdots \\
    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    (ii)
        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $K$-rooted.  
        Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
        $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
        $C'Qu=\rho(C')Qu$.

@@

\begin{proof}
    These assumptions are necessary that $PCQ \leq PC'Q$ where $P=I$,$Q=I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
     (\ref{lma_m_rooted}),\\
    $Q^{-1}C'Q$ = 
    $$\begin{pmatrix}
        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
        \vdots \\
        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    $Q^{-1}C'Q \geq 0$ for that $c'_{kj}\geq c'_{nj}>0$ when $1\leq j\leq n-1$ , $c'_{ij}\geq c_{ij}$ where $C$ is nonnegative,
    and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$\\

    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, \\
    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ \\
    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, \\
    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$ ;\\
    $C'$ is $K$-rooted matrix, then by Lemma (\ref{lma_m_rooted}) Conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3}, there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;\\
    And since $C$ is nonnegative, by Theorem~(\ref{thm:Perron_Frobenius}), which is Perron–Frobenius theorem, we claim there exists
    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ 
    is an eigenvalue of $C$ with associated left eigenvector $v^T$; \\
    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0.$, unless they are orthogonal, i.e, $v^Tv'=0$.\\[1ex]
    Here we can summarize the facts we know so far as the following: \\
    \begin{enumerate}[label=(\roman*)]
        \item  $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
        \item $v^Tv'>0.$
    \end{enumerate}
    which come from Theorem~(\ref{thm_main}).\\
    By Lemma~(\ref{l_diag}), for certain $d$, if $C'+dI$ is $K$-rooted, then it has
    a $K$-rooted eigenvector with its spectral radius $\lambda + d$. $C'$ would share the same
    eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
    conditions of Theorem~(\ref{thm_main}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
    then $\rho(C') \geq \rho(C)$  %\qed
\end{proof}

\subsection{Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    And its corresponding graph,\cite[sage]{sage}\\
    \includegraphics{graph_C.PNG} \\
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$

    also, graph,\cite[sage]{sage}\\
    \includegraphics{graph_Cprime.PNG} \\
    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of Theorem~\ref{thm_main},
    Then
    $\rho(C)\leq \rho(C')$ by previous Theorem~\ref{thm:conclusion}.
